Device fingerprinting for user authentication in web applications \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-16 paper.tex
Removed 'hash' from conclusion

\section{Conclusion}
In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique hashed fingerprints.

By combining various components of a device's properties, we could increase the fingerprint entropy as well as obtain a hash unqiue for an individual's device, correspondingly unique to an individual.

>>>>

\section{Conclusion}
In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique fingerprints.

By combining various components of a device's properties, we could increase the fingerprint entropy for an individual's device, correspondingly unique to an individual.
